Type theories as quotient inductive-recursive types

### 2025-02-26 tex/main.tex
no message

\subparagraph*{Implementing overlapping patterns via rewrite rules}
%The mechanism of defining a function by overlapping patterns is only implemented in an outdated experimental fork of \Agda.
To emulate a function by overlapping patterns, we declare each function clause a rewrite, together with another rewrite to identify the witness as the reflexivity proof $\mathsf{refl}$.
For example, the first few clauses for type substitution (written $[\sigma]_{\Ty}\,A$ rather than $\subTy{A}{\sigma}$ in the formalisation) are defined as
\begin{lstlisting}
postulate
  [_]_      : Sub Γ Δ → Ty Δ → Ty Γ
  [id]      : [ idS ]    A ≡ A
  {-# REWRITE [id]      #-}
  [id]≡refl : [id] {A = A} ≡ refl
  {-# REWRITE [id]=refl #-}
\end{lstlisting}
where \lstinline|[id]≡refl| ensures that \lstinline|[id]| disappears in transports.
We also turn on the option \texttt{-{}-local-confluence-check}  to check local confluence.
%
Overlapping patterns is indeed one of the use cases of user-defined rewrite rules discussed by Cockx~\cite{Cockx2020}.
The caveat, though, is that the termination checking is not imposed, so we need to check termination informally.

>>>>

\subparagraph*{Implementing overlapping patterns via rewrite rules}
%The mechanism of defining a function by overlapping patterns is only implemented in an outdated experimental fork of \Agda.
To emulate a function by overlapping patterns, we implement each function clause as a rewriting rule, together with another rule to identify the clause as the reflexivity proof $\mathsf{refl}$ (which ensures that the named function clause is merely synonymous with \lstinline|refl|).
For example, the first few clauses for type substitution (written $[\sigma]_{\Ty}\,A$ rather than $\subTy{A}{\sigma}$ in the formalisation) are defined as
\begin{lstlisting}
postulate
  [_]_      : Sub Γ Δ → Ty Δ → Ty Γ
  [id]      : [ idS ]    A ≡ A
  {-# REWRITE [id]      #-}
  [id]=refl : [id] {A = A} ≡ refl
  {-# REWRITE [id]=refl #-}
\end{lstlisting}
We also turn on the option \texttt{-{}-local-confluence-check} to check local confluence globally.
%
Overlapping patterns is indeed one of the use cases of user-defined rewrite rules discussed by Cockx~\cite{Cockx2020}.
The caveat, though, is that the termination checking is not imposed, so we need to check termination informally.
